---
output:
  md_document:
    variant: markdown_github
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## The problem

Here is the problem we'd like to solve.

- We would like to have all warnings to be errors so that we can deal with them.
- We use third party packages which sometimes throw warnings. These warnings do
not make us happy, but they should not break in production. We know them and
want to accept them.
- We use `parallel::mclapply` because we have some long running tasks and
realize `suppressWarnings` and `options(warn = 2)` do not work as expected in
parallel! Also, interactive sessions behave differently than batch mode.
All this is very tricky to resolve.

```{r}
options(warn = 0)
productionFunction <- function(x) {
  if (x == 1) suppressWarnings(warning("this may be okay"))
  ## just like *real* production code...
  else if (x == 2) stop("We should never end up in this branch...")
  else cbind(1:2, 1:3) # this is not okay and should be an error!
}

res <- parallel::mclapply(1:3, productionFunction, mc.cores = 2)
str(res)
options(warn = 2)
res1 <- parallel::mclapply(c(1, 3), productionFunction, mc.cores = 2)
str(res1)
```

Do you see the problem? Where was that error again? (Please notice, that if you
try to reproduce these results in an interactive session, you won't even get a
result back from `mclapply`.) Terrible indeed! I hear you. Fear not, there is a
solution...

## The salvation

Use `mcMap` as a drop in replacement for `mclapply` if you need more control
over errors and warnings. Be aware that `mcMap` is a simple wrapper around
`mclapply` and is not a novel parallel computing interface.

```{r}
library(mctools)
options(warn = 2)
```

Capture warnings and process them as you wish:

```{r}
mcMap(1:3, productionFunction)
```

White-list specific warnings if that is what you want:

```{r}
mcMap(1:3, productionFunction, warningsWhitelist = "multiple")
```

Or fail when any of the processes encounter warnings:

```{r error = TRUE}
mcMap(1:3, productionFunction, finallyStop = TRUE)
```

